The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2024-06-11 _tex/index.tex
Built site for gh-pages

    \begin{tabular*}{\textwidth}{@{}lllll@{}}
    \toprule
        ~ & T1w & T2w & pcASL & SWI \\ \midrule
        Sequence & 3D FSPGR & 3D CUBE & \makecell[tl]{Multi-shot 3D fast \\ spin-echo} & \makecell[tl]{3D spoiled GRE \\ flow-compensated} \\
        \makecell[tl]{Phase-encoding \\ direction} & Coronal & Sagittal & Axial & Axial \\
        TR (ms) & 7.74 & 2,300 & 4,680 & 30.9 \\
        TE (ms) & 2.97 & 66.29 & 10.55 & 5.24 \\
        Flip angle & 12$^{\circ}$ & 90$^{\circ}$ & 111$^{\circ}$ & 20$^{\circ}$ \\
        FOV (cm) & 20 & 20 & 24 & 25 \\
        Acquisition matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256 \\
        \makecell[tl]{In-plane resolution \\ (mm)} & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 & 0.977 x 0.977 \\
        \makecell[tl]{Slice thickness \\ (mm)} & 1 & 1 & 4 & \makecell[tl]{2, reconstructed \\ to 1 with zero \\ filling (ZIP2)} \\
        Number of slices & 126 & 106 & 50 & 92 \\
        Additional parameters & n/a & n/a & \makecell[tl]{1,450 ms label period; \\ 2,025 ms pulse label; \\ 24 control-label pairs} & n/a \\
        Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s \\ \botrule
    \end{tabular*}
    \footnotetext{T1w = T1-weighted; T2w = T2-weighted; pcASL = pseudo-continuous arterial spin labelling; SWI = susceptibility weighted imaging; FSPG = fast spoiled gradient echo; CUBE = General Electric name of sequence, not an acronym; GRE = gradient echo; ZIP2 = through-plane zero filling interpolation}

@@

    \begin{tabular}{@{}llllll@{}}
    \toprule
        Region & Measure & QSM & \makecell[tl]{Paramagnetic \\ map} & p-value & 95\% CI \\ \midrule
        \multirow{ 2}{*}{SSS} & Chi (ppm)     & 0.1 \pm 0.02                     & 0.21 \pm 0.05                     & \ensuremath{2.84\times 10^{-11}}                        & -0.13, -0.09           \\
                              & SvO$_{2}$(\%) & 72.46 \pm 3.43 & 58.14 \pm 7.3 & \ensuremath{6.12\times 10^{-10}} & 11.78, 16.85 \\
        \multirow{ 2}{*}{CCV} & Chi (ppm)     & 0.13 \pm 0.02             & 0.22 \pm 0.05             & \ensuremath{6.25\times 10^{-9}}                        & -0.1, -0.07           \\
                              & SvO$_{2}$(\%) & 68.71 \pm 3.46 & 57.69 \pm 6.97 & \ensuremath{2.16\times 10^{-9}} & 8.9, 13.13 \\
        \botrule
    \end{tabular}
    \footnotetext{QSM = quantitative susceptibility mapping; CI = confidence interval; SSS = superior sagitall sinus; CCV = central cerebral vein}

>>>>

    \begin{tabular*}{\textwidth}{@{}p{2.5cm}llp{2.5cm}p{2.5cm}@{}}
    \toprule
        ~ & T1w & T2w & pcASL & SWI \\ \midrule
        Sequence & 3D FSPGR & 3D CUBE & Multi-shot 3D fast spin-echo & 3D spoiled GRE flow-compensated \\
        Phase-encoding direction & Coronal & Sagittal & Axial & Axial \\
        TR (ms) & 7.74 & 2,300 & 4,680 & 30.9 \\
        TE (ms) & 2.97 & 66.29 & 10.55 & 5.24 \\
        Flip angle & 12$^{\circ}$ & 90$^{\circ}$ & 111$^{\circ}$ & 20$^{\circ}$ \\
        FOV (cm) & 20 & 20 & 24 & 25 \\
        Acquisition matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256 \\
        In-plane resolution (mm) & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 & 0.977 x 0.977 \\
        Slice thickness (mm) & 1 & 1 & 4 & 2, reconstructed to 1 with zero filling (ZIP2) \\
        Number of slices & 126 & 106 & 50 & 92 \\
        Additional parameters & n/a & n/a & 1,450 ms label period; 2,025 ms pulse label; 24 control-label pairs & n/a \\
        Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s \\ \botrule
    \end{tabular*}
    \footnotetext{T1w = T1-weighted; T2w = T2-weighted; pcASL = pseudo-continuous arterial spin labelling; SWI = susceptibility weighted imaging; FSPG = fast spoiled gradient echo; CUBE = General Electric name of sequence, not an acronym; GRE = gradient echo; ZIP2 = through-plane zero filling interpolation}

@@

    \begin{tabular}{@{}lllp{2cm}ll@{}}
    \toprule
        Region & Measure & QSM & Paramagnetic map & p-value & 95\% CI \\ \midrule
        \multirow{ 2}{*}{SSS} & Chi (ppm)     & 0.1 \pm 0.02                     & 0.21 \pm 0.05                     & \ensuremath{2.84\times 10^{-11}}                        & -0.13, -0.09           \\
                              & SvO$_{2}$(\%) & 72.46 \pm 3.43 & 58.14 \pm 7.3 & \ensuremath{6.12\times 10^{-10}} & 11.78, 16.85 \\
        \multirow{ 2}{*}{CCV} & Chi (ppm)     & 0.13 \pm 0.02             & 0.22 \pm 0.05             & \ensuremath{6.25\times 10^{-9}}                        & -0.1, -0.07           \\
                              & SvO$_{2}$(\%) & 68.71 \pm 3.46 & 57.69 \pm 6.97 & \ensuremath{2.16\times 10^{-9}} & 8.9, 13.13 \\
        \botrule
    \end{tabular}
    \footnotetext{QSM = quantitative susceptibility mapping; CI = confidence interval; SSS = superior sagitall sinus; CCV = central cerebral vein}
